---
title: "Jobs for a green recovery"
author: ""
output:
  flexdashboard::flex_dashboard:
    logo: GA_logo_RGB.png
    theme: paper
    css: styles.css
---

```{r setup, include=FALSE}
#Green Alliance dashboard

library(tidyverse)
library(shiny)
library(crosstalk)
library(flexdashboard)
library(sf)
library(leaflet)
library(leaflet.extras)
library(reactable)
library(downloadthis)
library(htmltools)
library(leafpm)
library(rgdal)

#Read in data
df.sf <- readRDS("GA_DB.RDS")

df.sf$`Share of woodland`<- recode_factor(df.sf$`Share of woodland`,
"Very high (27,500 to 45,800)" = "Very high",
"High (18,500 to 27,500)" = "High",
"Mid ( 9,500 to 16,500)" = "Mid",
"Low ( 4,300 to  9,300)" = "Low",
"Very low (     0 to  4,300)" = "Very low")





#download data
df <- st_drop_geometry(df.sf)
df <- as_tibble(df)
df <- df %>% dplyr::select(-cols, -LM2cols, -LM3cols, -LM4cols)
#df <- df[,-c(15:18)]

df.sf <- st_transform(df.sf, 4326)

df.sp <- df.sf %>% as('Spatial')

df.centroids <- df.sf %>% st_centroid()
df.centroids$lng <- st_coordinates(df.centroids)[,1]
df.centroids$lat <- st_coordinates(df.centroids)[,2]



sd <- SharedData$new(df,
                     #key = df$pcon19cd
                     )

sd.map <- SharedData$new(df.sp,
                     #key = df.sp@data$pcon19cd, 
                     group = sd$groupName()
                     
)

sd.centroids <- SharedData$new(df.centroids,
                              # key = ~pcon19cd, 
                               group = sd$groupName() )


#Pcon shapefile for linking

#pcon.bounds <- readOGR(dsn = "../Pcon 19 shapefile/", layer = "Westminster_Parliamentary_Constituencies_(December_2019)_Boundaries_UK_BUC" )
#pcon.bounds <- spTransform(pcon.bounds, CRS("+init=epsg:4326"))

pcon.bounds <- readRDS("GA_DB.RDS")
pcon.bounds <- pcon.bounds %>% as('Spatial')


#pcon.bounds <- sp::merge(pcon.bounds, df[,c(1,3)], by = "pcon19cd")

sd.pcon.bounds <- SharedData$new(pcon.bounds,
                                 #key = ~pcon19cd,
                                 group = sd$groupName())

#Seagrass points layer
seagrass.points <- readRDS( file = "seagrass.points.RDS")
seagrass.points <- st_transform(seagrass.points, 4326)
seagrass.points$lng <- st_coordinates(seagrass.points)[,1]
seagrass.points$lat <- st_coordinates(seagrass.points)[,2]
seagrass.points <- st_drop_geometry(seagrass.points)

# sd.seagrass <- SharedData$new(seagrass.points,
#                               key = ~pcon19cd,
#                               group = sd$groupName() )


Coastal.resto <- readRDS(file = "Coastal.resto.RDS")
# sd.coastal.resto <- SharedData$new(Coastal.resto,
#                               key = ~pcon19cd,
#                               group = sd$groupName() )

GNbogs.pcons <- readRDS(file = "../pcons.GN.bog.rds")

GNbogs.pcons <- st_transform(GNbogs.pcons, 4326)

GNbogs <- readRDS("../Great north bog areas.RDS")
GNbogs <- st_union(GNbogs)
GNbogs <- st_transform(GNbogs, 4326)
GNbogs <- st_as_sf(GNbogs)

# GNbogs.hidden.points <- readRDS(file = "../pcons.GN.bog.rds")
# GNbogs.hidden.points <- st_centroid(GNbogs.hidden.points)
# sd.GNbogs.hidden.points <- SharedData$new(GNbogs.hidden.points,
#                               key = ~pcon19cd,
#                               group = sd$groupName() )



woodland.pcon <- readRDS(file = "../Woodland.pcon.summary.RDS")
woodland.pcon <- woodland.pcon %>% filter(`Cumulative % share of woodland` %in% c("Very high (27,500 to 45,800)","High (18,500 to 27,500)"))
woodland.pcon <- woodland.pcon %>% dplyr::select(pcon19cd, `Cumulative % share of woodland`, `Woodland area (ha)`, long, lat)



woodland.pcon$`Cumulative % share of woodland` <- recode_factor(woodland.pcon$`Cumulative % share of woodland`,
"Very high (27,500 to 45,800)" = "Very high",
"High (18,500 to 27,500)" = "High",
"Mid ( 9,500 to 16,500)" = "Mid",
"Low ( 4,300 to  9,300)" = "Low",
"Very low (     0 to  4,300)" = "Very low")

woodland.pcon.hidden <- woodland.pcon %>% st_centroid()
woodland.pcon <- st_union(woodland.pcon)


sd.woodland.pcon.hidden <- SharedData$new(woodland.pcon.hidden,
                                          key = ~pcon19cd,
                              group = sd$groupName() ) 

```

Maps and data {data-icon="ion-stats-bars"}
=====================================  

Column {data-width=975}
-------------------------------------

#### Background

In 2021, Green Alliance commissioned WPI Economics to research the link between restoring nature and levelling up. Their analysis calculates a labour market challenge score for each constituency and finds that those with the greatest challenges also have the greatest potential for nature restoration. 

[Policy recommendations](https://green-alliance.org.uk/resources/Jobs_for_a_green_recovery.pdf)

[Full report – Economics of enhancing the natural environment](https://green-alliance.org.uk/resources/Green_renewal_WPI.pdf)


### Search by constituency name
    
```{r datatable}

area.search <- filter_select(
  id = "geo_pcon",
  label = NULL,
  sharedData = sd,
  group = ~`Constituency`
)


tbl <- reactable(sd, #selection = "single",
                 onClick = "select",
                 rowStyle = list(cursor = "pointer"),
                 #minRows = 10,
                 filterable = F,
                 searchable = F, wrap = T, pagination = FALSE, striped = T, highlight = T,
                 defaultSorted = list("Constituency" = "asc"),
                 defaultColDef = colDef(align = "center"),
                columns = list(
                          pcon19cd = colDef(show = F),
                          Constituency = colDef(align = "left"),
                          #`Labour market challenge score (100 = average)`= colDef(filterable = F),
                          #`Forecast change in employments 2019-2025 (%)`= colDef(filterable = F),
                          #`Underemployment Sept 2019 (% 16-64)`= colDef(filterable = F),
                          #`Underemployment change Sept 2019 - Sept 2020 (%)`= colDef(filterable = F),
                          #`Known Seagrass location within 1000m` = colDef(filterable = T),s
                          `Woodland area (ha)` = colDef(filterable = F, format = colFormat(separators = T)),
                          `Share of woodland` = colDef(filterable = F, show = F),

                          `Priority sites coastal restoration sites (count)` = colDef(show = F),
                          `All coastal restoration sites (count)` = colDef(show = F),

                          #`Coastal restoration sites flag` = colDef(filterable = T),
                          #`Coastal restoration priority sites flag` = colDef(filterable = T),
                          #`Within 20 miles of Great North Bog` = colDef(filterable = T),

                            #geometry = colDef(show = F),
                          `Coastal restoration priority sites flag`  = colDef(show = F),
                            cols = colDef(show = F),
                            LM2cols = colDef(show = F),
                            LM3cols = colDef(show = F),
                            LM4cols = colDef(show = F)
                          ),



                 #`COVID-19 deaths per 100,000` = colDef(aggregate = "mean",format = colFormat(digits = 0)),
                 #`COVID-19 deaths age adjusted per 100,000` = colDef(aggregate = "mean",format = colFormat(digits = 0))),
                 theme = reactableTheme(
                   stripedColor = "#f3f5f4",
                   highlightColor = "#C3CDC8",
                   cellPadding = "4px 8px",
                   style = list(fontFamily = "Franklin Gothic Book", fontSize = "9px"),
                   #searchInputStyle = list(width = "100%", fontWeight = "400"),
                   headerStyle = list(color = "white",background = "#54716E", weight = "normal", fontSize = "9px",
                                      "&:hover[aria-sort]" = list(background = "#C3CDC8"),
                                      "&[aria-sort='ascending'], &[aria-sort='descending']" = list(background = "#C3CDC8"),
                                      borderColor = "#00946E"
                   )
                 ))


#Alternative using DT
# 
#  tbl <-   sd %>%  
#       DT::datatable(
#         filter = "top",  # allows filtering on each column
#         height = "100%",
#         fillContainer = TRUE,
#         extensions = c(
#           "Buttons",  # add download buttons, etc
#           "Scroller"  # for scrolling down the rows rather than pagination
#         ),
#         rownames = FALSE,  # remove rownames
#         #style = "bootstrap",
#         class = "cell-border stripe",
#         width = "100%",
#         options = list(
#           dom = "Blrtip",  # specify content (search box, etc)
#           deferRender = TRUE,
#           scrollY = 300,
#           scroller = TRUE,
#           
#           columnDefs = list(
#             list(
#               visible = FALSE,
#               targets = list(0,9,10,14)
#             )
#           ), 
#           buttons = list(
#             I("colvis"),  # turn columns on and off
#             "csv",  # download as .csv
#             "excel"  # download as .xlsx
#           )
#         )
#       )


dl.button <- df %>%
  download_this(
    output_name = "Economics of natural environment",
    output_extension = ".csv",
    button_label = "Download data as csv",
    button_type = "default",
    has_icon = TRUE,
    icon = "fa fa-save"
  )

dl.button.xl <- df %>%
  download_this(
    output_name = "Economics of natural environment",
    output_extension = ".xlsx",
    button_label = "Download data as EXCEL",
    button_type = "default",
    has_icon = TRUE,
    icon = "fa fa-save"
  )

combo <- htmltools::tagList(area.search,dl.button,dl.button.xl,tbl) 
combo

```


Column {data-width=125}{.tabset}
-------------------------------------

### LM Challenge

```{r map}

#Adds LM challenge colours as variable

rad <- 3

cols <- c("#f0cfc7",
          "#dca091",
          "#c4725f",
          "#a94330",
          "#8a0000")



LM2cols <- c("#8a0000",
          "#c98271",
          "#E0E0E0",
          "#adb8e6",
          "#7081e4")

LM4cols <- c("#adb8e6", #blue
          "#ebc3b9",
          "#d18978",
          "#b04f3b",
          "#8a0000")

LM3cols <- cols

meanval <- mean(df.sf$`Labour market challenge score (100 = average)`)
sdval <- sd(df.sf$`Labour market challenge score (100 = average)`)

#written long
very.high <- paste0("Greater than ",round(meanval + (sdval*1.5),0))
high <- paste0("Greater than ",round(meanval + (sdval*0.5),0) , " and less than ",round(meanval + (sdval*1.5),0)   )
average <- paste0("Greater than ",round(meanval - (sdval*0.5),0) , " and less than ",round(meanval + (sdval*0.5),0)  )
low <- paste0("Greater than ", round(meanval - (sdval*1.5),0), " and less than ", round(meanval - (sdval*0.5),0)  )
very.low <- paste0("Less than ", round(meanval - (sdval*1.5) ,0))

long.cats <- c(very.high, high, average, very.low, low)

#condensed
very.high.sht <- paste0("> ",round(meanval + (sdval*1.5),0))
high.sht <- paste0("> ",round(meanval + (sdval*0.5),0) , " <= ",round(meanval + (sdval*1.5),0)   )
average.sht <- paste0("> ",round(meanval - (sdval*0.5),0) , " <= ",round(meanval + (sdval*0.5),0)  )
low.sht <- paste0("> ", round(meanval - (sdval*1.5),0), " <= ", round(meanval - (sdval*0.5),0)  )
very.low.sht <- paste0("<= ", round(meanval - (sdval*1.5) ,0))

short.cats <- c(very.high.sht, high.sht, average.sht, very.low.sht, low.sht)




labels1 <- sprintf("<strong>%s</strong><br/>Challenge score: %s<sup></sup><br/>",
                   df.sf$Constituency, df.sf$`Labour market challenge score (100 = average)`) %>%
  lapply(htmltools::HTML)

labels2 <- sprintf("<strong>%s</strong><br/>Forecast change in employments: %s<sup></sup><br/>",
                   df.sf$Constituency, df.sf$`Forecast change in employments 2019-2025 (%)`) %>%
  lapply(htmltools::HTML)

labels3 <- sprintf("<strong>%s</strong><br/>Underemployment pre-pandemic: %s<sup></sup><br/>",
                   df.sf$Constituency, df.sf$`Underemployment Sept 2019 (% 16-64)`) %>%
  lapply(htmltools::HTML)

labels4 <- sprintf("<strong>%s</strong><br/>Underemployment change: %s<sup></sup><br/>",
                   df.sf$Constituency, df.sf$`Underemployment change Sept 2019 - Sept 2020 (%)`) %>%
  lapply(htmltools::HTML)


plot <- leaflet(sd.map, options= leafletOptions(padding = 100, zoomSnap = 0.25, zoomDelta = 0.3, zoomControl = T, minZoom = 5.3)) %>%
  setView(lng =  -3.13,
          lat = 54.8, zoom = 5.7) %>% #setView gives centre coordinates and zoom level
  
  setMapWidgetStyle(list(background = "white")) %>%
  
  #add panes to control priority order of layers
  addMapPane(name = "basemap", zIndex = 410) %>% 
  addMapPane(name = "overlays", zIndex = 420) %>% 
  
  addProviderTiles(providers$CartoDB.Positron, providerTileOptions(opacity = 0.1),
                   options = providerTileOptions(minZoom = 9, maxZoom = 15)) %>%
  
  
  addPolygons(data = sd.pcon.bounds, 
              stroke = T,
              color = "black",
              weight = 1.5,
              fillOpacity = 0) %>% 
  
  
  #hidden markers for selection filtering
  addCircleMarkers(data = sd.centroids, 
                   group = "hidden",
                   lng = ~lng, lat = ~lat,
                   radius = rad,
                   weight = 0,
                   opacity = 1,
                   fillOpacity = 1,
                   fillColor = "blue"
                  
  ) %>%
  
  
  addPolygons( stroke = T, color = "white",
               group = "LM Challenge",
               fillColor = ~cols,
               opacity = 0.5,
               fillOpacity = 0.7, weight = 0.25, label = labels1,
              
               highlight= highlightOptions(color="white", weight=2, bringToFront= T),
               options = leafletOptions(pane = "basemap"))  %>%
  
  
  addCircleMarkers(data = seagrass.points, lng = ~lng, lat = ~lat, group =  "Seagrass points",
                   radius = rad,
                   weight = 0,
                   fillOpacity = 1,
                   fillColor = "#006784",
                   options = leafletOptions(pane = "overlays"),
                   popup = ~PlaceName
  ) %>%
  
  addCircleMarkers(data = Coastal.resto, lng = ~lng, lat = ~lat, group =  "Coastal restoration sites",
                   radius = rad,
                   weight = 0,
                   fillOpacity = 1,
                   fillColor = "#EE2E24",
                  options = leafletOptions(pane = "overlays"),
                  popup = ~Site_Name
  ) %>%
  
  
  addPolygons(data = GNbogs, stroke = T, color = "#E2D148",
              group = "Great North Bog",
              fillColor = "white",
              opacity = 1,
              fillOpacity = 0, weight = 1.75, 
              options = leafletOptions(pane = "overlays")
  )  %>%
  
  

  addPolygons(data = woodland.pcon, stroke = T, color = "#77A88C",
              group = "High woodland potential",
              fillColor = "white",
              opacity = 1,
              fillOpacity = 0, weight = 2,
              options = leafletOptions(pane = "overlays")
  )  %>%
  
    addResetMapButton() %>% 
  

  addLayersControl(overlayGroups = c("Seagrass points",
                                     "Coastal restoration sites",
                                     "Great North Bog",
                                     "High woodland potential"),
                                                                         
                   options = layersControlOptions(collapsed = FALSE),
                   position = "topright") %>%
  
  hideGroup(c("Seagrass points",
              "Coastal restoration sites",
              "Great North Bog",
              "High woodland potential",
              "hidden"
              )) %>%
  

  
  addLegend(group = "LM Challenge",
            colors = rev(cols),
            labels = c(
              paste0("Very high (", very.high.sht,")"),
              paste0("High (",high.sht,")"),
              paste0("Average (",average.sht,")"),
              paste0("Low (", low.sht,")"),
              paste0("Very low (",very.low.sht,")")
            ),
            position = "topright",
            title="Labour market challenge score",
            opacity=0.65) 






# plot <- leaflet(sd.centroids, options= leafletOptions(padding = 100, zoomSnap = 0.25, zoomDelta = 0.3, zoomControl = T)) %>%
#   setView(lng =  -3.13,
#           lat = 54.8,zoom = 5.3) %>% #setView gives centre coordinates and zoom level
#
#   setMapWidgetStyle(list(background = "white")) %>%
#
#   addPolygons(data = df.sf, stroke = T, color = "white",
#               #layerId = ~pcon19cd,
#               fillColor = ~cols,
#               opacity = 1,
#               fillOpacity = 1, weight = 0.25, label = labels1,
#               highlight= highlightOptions(color="white", weight=2, bringToFront= T))  %>%
#
#   addCircleMarkers(radius = 3, weight = 0, fillOpacity = 1, fillColor = "#00946E") %>%
#
#   removeDrawToolbar()
#
#
 plot



```

### Employment forecast

```{r map2}

plot <- leaflet(sd.map, options= leafletOptions(padding = 100, zoomSnap = 0.25, zoomDelta = 0.3, zoomControl = T, minZoom = 5.3)) %>%
  setView(lng =  -3.13,
          lat = 54.8,zoom = 5.7) %>% #setView gives centre coordinates and zoom level
  
  setMapWidgetStyle(list(background = "white")) %>%
  
  addProviderTiles(providers$CartoDB.Positron, providerTileOptions(opacity = 0.1),
                   options = providerTileOptions(minZoom = 9, maxZoom = 15)) %>%
  
    #add panes to control priority order of layers
  addMapPane(name = "basemap", zIndex = 410) %>% 
  addMapPane(name = "overlays", zIndex = 420) %>% 
  
  
  addCircleMarkers(data = sd.centroids, lng = ~lng, lat = ~lat, group =  "LM Challenge",
                   radius = rad,
                   weight = 0,
                   opacity = 0,
                   fillOpacity = 0,
                   fillColor = "blue"
  ) %>%
  
  
 
    addPolygons( stroke = T, color = "white",
               group = "Employment change forecast",
               fillColor = ~LM2cols,
               opacity = 0.5,
               fillOpacity = 1, weight = 0.25, label = labels2,
               highlight= highlightOptions(color="white", weight=2, bringToFront= T))  %>%
  
addCircleMarkers(data = seagrass.points, lng = ~lng, lat = ~lat, group =  "Seagrass points",
                   radius = rad,
                   weight = 0,
                   fillOpacity = 1,
                   fillColor = "#006784",
                   options = leafletOptions(pane = "overlays"),
                   popup = ~PlaceName
  ) %>%
  
  addCircleMarkers(data = Coastal.resto, lng = ~lng, lat = ~lat, group =  "Coastal restoration sites",
                   radius = rad,
                   weight = 0,
                   fillOpacity = 1,
                   fillColor = "#EE2E24",
                  options = leafletOptions(pane = "overlays"),
                  popup = ~Site_Name
  ) %>%
  
  
  addPolygons(data = GNbogs, stroke = T, color = "#E2D148",
              group = "Great North Bog",
              fillColor = "white",
              opacity = 1,
              fillOpacity = 0, weight = 1.75, 
              options = leafletOptions(pane = "overlays")
  )  %>%
  
  

  addPolygons(data = woodland.pcon, stroke = T, color = "#77A88C",
              group = "High woodland potential",
              fillColor = "white",
              opacity = 1,
              fillOpacity = 0, weight = 2,
              options = leafletOptions(pane = "overlays")
  )  %>%
  

  addLayersControl(overlayGroups = c("Seagrass points",
                                     "Coastal restoration sites",
                                     "Great North Bog",
                                     "High woodland potential"),
                                                                         
                   options = layersControlOptions(collapsed = FALSE),
                   position = "topright") %>%
  
  hideGroup(c("Seagrass points",
              "Coastal restoration sites",
              "Great North Bog",
              "High woodland potential"
              )) %>%
  
  addResetMapButton() %>% 
  
  
  
  addLegend(group = "Employment change forecast",
            colors = rev(LM2cols), 
            labels = c(
              "Very high", 
              "High", 
              "Average", 
              "Low",
              "Very low"
            ),
            position = "topright",
            title="Forecast change <br>in employments (%)",
            opacity=1) 
  plot

```
### Underemployment 2019

```{r map3}
plot <- leaflet(sd.map, options= leafletOptions(padding = 100, zoomSnap = 0.25, zoomDelta = 0.3, zoomControl = T, minZoom = 5.3)) %>%
  setView(lng =  -3.13,
          lat = 54.8,zoom = 5.7) %>% #setView gives centre coordinates and zoom level
  
  setMapWidgetStyle(list(background = "white")) %>%
  
  addProviderTiles(providers$CartoDB.Positron, providerTileOptions(opacity = 0.1),
                   options = providerTileOptions(minZoom = 9, maxZoom = 15)) %>%
  
    #add panes to control priority order of layers
  addMapPane(name = "basemap", zIndex = 410) %>% 
  addMapPane(name = "overlays", zIndex = 420) %>% 
  
  addCircleMarkers(data = sd.centroids, lng = ~lng, lat = ~lat, group =  "LM Challenge",
                   radius = rad,
                   weight = 0,
                   opacity = 0,
                   fillOpacity = 0,
                   fillColor = "blue"
  ) %>%
  
  

  addPolygons( stroke = T, color = "white",
               group = "Underemployment pre-pandemic",
               fillColor = ~LM3cols,
               opacity = 0.5,
               fillOpacity = 1, weight = 0.25, label = labels3,
               highlight= highlightOptions(color="white", weight=2, bringToFront= T))  %>%
  

  
  
  addCircleMarkers(data = seagrass.points, lng = ~lng, lat = ~lat, group =  "Seagrass points",
                   radius = rad,
                   weight = 0,
                   fillOpacity = 1,
                   fillColor = "#006784",
                   options = leafletOptions(pane = "overlays"),
                   popup = ~PlaceName
  ) %>%
  
  addCircleMarkers(data = Coastal.resto, lng = ~lng, lat = ~lat, group =  "Coastal restoration sites",
                   radius = rad,
                   weight = 0,
                   fillOpacity = 1,
                   fillColor = "#EE2E24",
                  options = leafletOptions(pane = "overlays"),
                  popup = ~Site_Name
  ) %>%
  
  
  addPolygons(data = GNbogs, stroke = T, color = "#E2D148",
              group = "Great North Bog",
              fillColor = "white",
              opacity = 1,
              fillOpacity = 0, weight = 1.75, 
              options = leafletOptions(pane = "overlays")
  )  %>%
  
  

  addPolygons(data = woodland.pcon, stroke = T, color = "#77A88C",
              group = "High woodland potential",
              fillColor = "white",
              opacity = 1,
              fillOpacity = 0, weight = 1.75,
              options = leafletOptions(pane = "overlays")
  )  %>%
  

  addLayersControl(overlayGroups = c("Seagrass points",
                                     "Coastal restoration sites",
                                     "Great North Bog",
                                     "High woodland potential"),
                                                                         
                   options = layersControlOptions(collapsed = FALSE),
                   position = "topright") %>%
  
  hideGroup(c("Seagrass points",
              "Coastal restoration sites",
              "Great North Bog",
              "High woodland potential"
              )) %>%
  
  addResetMapButton() %>% 
  
  
  addLegend(group =  "Underemployment pre-pandemic",
            colors = LM3cols, 
            labels = c(
              # "less than 5.7%",
              # "5.7% - 8.3%",
              # "8.3% - 11.0",
              # "11.0% - 13.6%",
              # "Greater than 13.6%"
              "Very low",
              "Low",
              "Average",
              "High",
              "Very high"
            ),
            labFormat = labelFormat(suffix = "%%"),
            position = "topright",
            title="Underemployment <br>
            Sept 2019 (16-64)",
            opacity=1) 
  plot

```

### Underemployment Change

```{r map4}
plot <- leaflet(sd.map, options= leafletOptions(padding = 100, zoomSnap = 0.25, zoomDelta = 0.3, zoomControl = T, minZoom = 5.3)) %>%
  setView(lng =  -3.13,
          lat = 54.8,zoom = 5.7) %>% #setView gives centre coordinates and zoom level
  
  setMapWidgetStyle(list(background = "white")) %>%
  
  addProviderTiles(providers$CartoDB.Positron, providerTileOptions(opacity = 0.1),
                   options = providerTileOptions(minZoom = 9, maxZoom = 15)) %>%
  
  
    #add panes to control priority order of layers
  addMapPane(name = "basemap", zIndex = 410) %>% 
  addMapPane(name = "overlays", zIndex = 420) %>% 
  
  addCircleMarkers(data = sd.centroids, lng = ~lng, lat = ~lat, group =  "LM Challenge",
                   radius = rad,
                   weight = 0,
                   opacity = 0,
                   fillOpacity = 0,
                   fillColor = "blue"
  ) %>% 
  
  addPolygons( stroke = T, color = "white",
               group = "Underemployment change",
               fillColor = ~LM4cols,
               opacity = 0.5,
               fillOpacity = 1, weight = 0.25, label = labels4,
               highlight= highlightOptions(color="white", weight=2, bringToFront= T))  %>%
  
  
  
  
  
  
  addCircleMarkers(data = seagrass.points, lng = ~lng, lat = ~lat, group =  "Seagrass points",
                   radius = rad,
                   weight = 0,
                   fillOpacity = 1,
                   fillColor = "#006784",
                   options = leafletOptions(pane = "overlays"),
                   popup = ~PlaceName
  ) %>%
  
  addCircleMarkers(data = Coastal.resto, lng = ~lng, lat = ~lat, group =  "Coastal restoration sites",
                   radius = rad,
                   weight = 0,
                   fillOpacity = 1,
                   fillColor = "#EE2E24",
                  options = leafletOptions(pane = "overlays"),
                  popup = ~Site_Name
  ) %>%
  
  
  addPolygons(data = GNbogs, stroke = T, color = "#E2D148",
              group = "Great North Bog",
              fillColor = "white",
              opacity = 1,
              fillOpacity = 0, weight = 1.5, 
              options = leafletOptions(pane = "overlays")
  )  %>%
  
  

  addPolygons(data = woodland.pcon, stroke = T, color = "#77A88C",
              group = "High woodland potential",
              fillColor = "white",
              opacity = 1,
              fillOpacity = 0, weight = 2,
              options = leafletOptions(pane = "overlays")
  )  %>%
  

  addLayersControl(overlayGroups = c("Seagrass points",
                                     "Coastal restoration sites",
                                     "Great North Bog",
                                     "High woodland potential"),
                                                                         
                   options = layersControlOptions(collapsed = FALSE),
                   position = "topright") %>%
  
  hideGroup(c("Seagrass points",
              "Coastal restoration sites",
              "Great North Bog",
              "High woodland potential"
              )) %>%
  
  addResetMapButton() %>% 
  
  
  
  addLegend(group = "Underemployment change",
            colors = LM4cols, 
            labels = c(
              "-30% - 0%",
              "0% - 30%",
              "30% - 60%",
              "60% - 90%",
              "90%+"
            ),
            labFormat = labelFormat(suffix = "%%"),
            position = "topright",
            title="Underemployment change<br>
            Sept 2019 to Sept 2020 (%)",
            opacity=1) 



plot


```

Information {data-orientation=rows data-icon="fa-info-circle"}
===================================== 

### Definitions 

#### Labour market challenge score
An index where 100 reflects the average constituency. It is constructed from four measures: underemployment before the pandemic; the increase in underemployment in the year to September 2020; the proportion of the working age population on furlough and SEISS in January 2021; forecast change in employment based on sectoral risk.

#### Seagrass points
Current and historic known seagrass meadows. This is where restoration is most likely needed but it is likely an underestimate. Seagrass locations were estimated by WPI Economics from named locations provided in [Green at al (2021)](https://www.frontiersin.org/articles/10.3389/fpls.2021.629962/full) but may not represent exact locations.

#### Coastal restoration
Potential sites for new coastal habitats, identified by the RSPB Sustainable Shores project.

#### Great North Bog
Outline of the Great North Bog proposal, a peatland restoration initiative being developed by the North Pennines AONB partnership, the Yorkshire Peat Partnership and the Moors for the Future partnership. There is no comprehensive, national mapping of peatland potential currently in the public domain, though the Great North Bog contains 92% of England’s upland peat.

#### High woodland potential
The constituencies with the highest potential for new woodland, with at least 18,500 hectares per constituency. Potential woodland sites were identified by the RSPB, avoiding carbon rich soils, important non-woodland habitats, nature conservation sites, highly productive farmland and towns and cities.

All further methodology and sources can be found in the [full report](https://green-alliance.org.uk/)

### How to use this app

#### Filters

You can:

* Select one or more constituencies from the dropdown menu (remove them with your backspace key)
* Filter the table from the spaces under the column headings
* Filter the table using the map selection tool

#### Interactive map

You can:

* click to grab and drag the map around
* zoom with the '+' and '--' buttons (top-left) or with your mouse's scroll wheel
* click an area to reveal a popup with information about that constituency
* click the button showing a broken square (top-left under the zoom options) to select points on the map using a window that's draggable (click and hold the grid icon in the upper left) and resizeable (click and drag the white boxes in each corner)

#### Interactive table

You can:

* filter each column by typing in the boxes under each column header
* sort the columns (ascending and descending) by clicking on the column header
* change which columns are visible by clicking the Column visibility button
* click 'CSV' or 'Excel' to download the filtered data to a .csv file or a .xlsx
* see how many entries remain after filtering in the bottom-left, where it says 'Showing X to Y of Z entries'

#### Tools used

[R v3.6.0](https://www.r-project.org/) and [RStudio v1.3.1093](https://www.rstudio.com/) were used to build this tool.

The packages used were:

* [Flexdashboard](https://rmarkdown.rstudio.com/flexdashboard/)
* [Leaflet](https://rstudio.github.io/leaflet/)
* [Reactable](https://glin.github.io/reactable/)
* [Crosstalk](https://rstudio.github.io/crosstalk/)
* [Downloadthis](https://www.rdocumentation.org/packages/downloadthis/versions/0.2.1)

### About us

#### Green Alliance
Green Alliance is an independent think tank and charity focused on ambitious leadership for the environment. Since 1979, Green Alliance has been working with the most influential leaders in business, NGOs and politics to accelerate political action and create transformative policy for a green and prosperous UK.

#### WPI Economics
WPI Economics is an economics and public policy consultancy. We are driven by a desire to make a difference, both through the work we undertake and by taking our responsibilities as a business seriously. We provide a range of public, private and charitable clients with research, economic analysis and advice to influence and deliver better outcomes through improved public policy design and delivery. 