---
title: "Economics of enhancing the natural environment"
author: ""
output:
  flexdashboard::flex_dashboard:
    logo: GA_logo_RGB900.png
    theme: paper
    css: styles.css
---

```{r setup, include=FALSE}


```

Maps and data {data-icon="ion-stats-bars"}
=====================================  

Column {data-width=850}
-------------------------------------

#### About this visualisation

This space here can be used to explain some background to the project etc.
This space here can be used to explain some background to the project etc.
This space here can be used to explain some background to the project etc.
This space here can be used to explain some background to the project etc.
This space here can be used to explain some background to the project etc.

<!-- ### Filters -->

<!-- ```{r filters} -->


<!-- bscols( -->
<!--   filter_checkbox( -->
<!--     id = "seagrass", -->
<!--     label = "Seagrass within 1000m", -->
<!--     sharedData = sd, -->
<!--     group = ~`Seagrass location within 1000m` -->
<!--   ), -->

<!--   filter_checkbox( -->
<!--     id = "woodland", -->
<!--     label = "Share of woodland (cum %)", -->
<!--     sharedData = sd, -->
<!--     group = ~`Share of woodland (cumulative %)` -->
<!--   ), -->
<!--   filter_checkbox( -->
<!--     id = "resto1", -->
<!--     label = "Coastal restoration sites", -->
<!--     sharedData = sd, -->
<!--     group = ~`Coastal restoration sites flag` -->
<!--   ), -->

<!--     filter_checkbox( -->
<!--     id = "RestoP", -->
<!--     label = "Coastal restoration priority sites", -->
<!--     sharedData = sd, -->
<!--     group = ~`Coastal restoration priority sites flag` -->
<!--   ), -->
<!--     filter_checkbox( -->
<!--     id = "bog", -->
<!--     label = "Within 20 miles of great north bog", -->
<!--     sharedData = sd, -->
<!--     group = ~`Within 20 miles of great north bog` -->
<!--   ) -->
<!-- ) -->

<!-- bscols( -->
<!--   filter_slider( -->
<!--     id = "LM score", -->
<!--     label = "Labour Market Challenge score (100 is average)", -->
<!--     width = "100%", -->
<!--     sharedData = sd, -->
<!--     column = ~`Labour market challenge score (100 = average)`) -->

<!--   ) -->


<!-- ``` -->

### Search by constituency name
    
```{r datatable}



```


Column {data-width=250}{.tabset}
-------------------------------------

### LM Challenge

```{r map}





```

### Employment forecast

```{r map2}



```
### Underemployment 2019

```{r map3}


```

### Underemployment Change

```{r map4}



```

Information {data-orientation=rows data-icon="fa-info-circle"}
===================================== 

### About 

Space to write something about Green Alliance and WPI perhaps?

### How to use this app

#### Filters

You can:

* Select one or more constituencies from the dropdown menu (remove them with your backspace key)
* Filter the table from the spaces under the column headings
* Filter the table using the map selection tool

#### Interactive map

You can:

* click to grab and drag the map around
* zoom with the '+' and '--' buttons (top-left) or with your mouse's scroll wheel
* click an area to reveal a popup with information about that constituency
* click the button showing a broken square (top-left under the zoom options) to select points on the map using a window that's draggable (click and hold the grid icon in the upper left) and resizeable (click and drag the white boxes in each corner)

#### Interactive table

You can:

* filter each column by typing in the boxes under each column header
* sort the columns (ascending and descending) by clicking on the column header
* change which columns are visible by clicking the Column visibility button
* click 'CSV' or 'Excel' to download the filtered data to a .csv file or a .xlsx
* see how many entries remain after filtering in the bottom-left, where it says 'Showing X to Y of Z entries'

### Tools

[R v3.6.0](https://www.r-project.org/) and [RStudio v1.3.1093](https://www.rstudio.com/) were used to build this tool.

The packages used were:

* [Flexdashboard](https://rmarkdown.rstudio.com/flexdashboard/) to create a frame for the content
* [Leaflet](https://rstudio.github.io/leaflet/) for the interactive map
* [Reactable](https://glin.github.io/reactable/) for the interactive table
* [Crosstalk](https://rstudio.github.io/crosstalk/) for widget interactivity
